PANCHANGE_data_preprocessing

### 2020-08-25 PANCHANGE_data_preprocessing2020-07-15.Rmd
added pcl percentages and made changes to the preprocessing script
add autism chunk for harmonising

>>>>

### Autism spectrum disorder
```{r mhd autism_spectrum_disorder}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE){
  mhd.raw.id <- mhd.raw.id %>%
    mutate(
      autism_spectrum_disorder_numeric =
        case_when(
          mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 0 ~ 0,
          mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric == 1 ~ 1
        )
    )

  mhd.raw.id <- mhd.raw.id %>%
    mutate(
      autism_spectrum_disorder =
        recode_factor(
          autism_spectrum_disorder_numeric,
          `0` = "No autism spectrum disorder",
          `1` = "Autism spectrum disorder"
        )
    )

  mhd.raw.id %>%
    freq(autism_spectrum_disorder)
}
```

```{r Check psychotic_disorders}
if(GLAD == TRUE | EDGI == TRUE | NBR == TRUE | RAMP == TRUE) {
mhd.raw.id %>%
  select(
    autism_spectrum_disorder,
    autism_spectrum_disorder_numeric,
    mhd.autism_aspergers_or_autistic_spectrum_disorder,
    mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric
  )
}
```

```{r}
mhd.raw.id %>%
  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder)

mhd.raw.id %>%
  freq(mhd.autism_aspergers_or_autistic_spectrum_disorder_numeric)
